Online Tuning of EASY-Backfilling using Queue Reordering Policies.

### 2018-01-08 paper/paper.tex
some changes

The above cost directly corresponds to the cumulative waiting time of the
policy over the preceding periods (more precisely to the cumulative simulated
estimate of the waiting time of the policy over the preceding periods) so that
the length of the period has little impact here. The only bias comes from the
boundary states of the simulation. Indeed, we run simulations from an empty
system and wait for the system to be empty when job submissions cease at the
end of the submission period.

Furthermore, in the context of this study and as detailed in
Section~\ref{sec:experiments}, we rely on averages over several execution
traces in order to obtain reliable estimate of the behavior of different
policies and policy selection strategies. Such traces are typically obtained by
simulation. Using the same simulator for generating the traces and estimating
the cost as defined in Eqs \eqref{eq:cost-exact} and \eqref{eq:tot-cost-exact}
would however be too optimistic and would represent an upper bound on what can
be achieved by a selection strategy based on simulation. In order to have a
more realistic estimate of the behavior of a selection strategy based on
simulation, we introduce noise in the simulator, as described below.

@@

%
\begin{itemize}
\item With probability $(1-\epsilon)$, select the policy $P$ that minimizes the cost over previous time periods (exploitation mode):
%
\begin{equation}
\label{eq:select-greedy}
P = \mbox{argmin}_{P_i, 1 \le i \le 12} w(\rightarrow T;P_i)
\end{equation}
%
\item With probability $\epsilon$, select a policy $P_i, \, 1 \le i \le 12$, at random (exploration mode).
\end{itemize}

Several studies study the decay of $\epsilon$ over time, the exploration being
less important once the estimates for the different policies are reliable
\cite{Tokic:2010}. This strategy has however not been beneficial in our case.
We believe this is due to the properties of the traces we use, as explained in
Section~\ref{sec:experiments}. The $\epsilon$-greedy strategy is known to be
outperformed in terms of regret by other classical algorithms such as the UCB
or EXP family of algorithms. See~\cite{bubnow} for a precise definition and
thorough treatment of this subject. These algorithms however all rely on
pre-normalized rewards. Here, the scale of $w_{\epsilon}(t;P_i)$ is not known
in advance. While the usual doubling tricks can be devised to go around
sequential issues of scale with good asymptotical performance, they ruin
performance in practice. Accordingly, we only perform experiments using the
simple $\epsilon$-greedy method.

>>>>

The above cost directly corresponds to the cumulative waiting time of the
policy over the preceding periods (more precisely to the cumulative simulated
estimate of the waiting time of the policy over the preceding periods) so that
the length of the period has little impact here. The only bias comes from the
boundary states of the simulation. Indeed, we run simulations from an empty
system and wait for the system to be empty when job submissions cease at the
end of the submission period. Figure~\ref{fig:resimu}

\begin{figure*}[]
  \centering
  \input{dia/_build/algo.tex}

  \caption{Illustration of the online simulation-based strategy. Every week,
  the wokload from the past week is used to run simulations using every
  reordering policy. The "model" $w$ is updated according
  to~\eqref{eq:tot-cost-exact} (or~\eqref{eq:tot-cost-noisy} in the Noisy case
  from Section~\ref{sub:noisy}) and the policy for the next week is chosen
  according to~\eqref{eq:select-exact}}.

  \label{fig:resimu}
\end{figure*}

Furthermore, in the context of this study and as detailed in
Section~\ref{sec:experiments}, we rely on averages over several execution
traces in order to obtain reliable estimate of the behavior of different
policies and policy selection strategies. Such traces are typically obtained by
simulation. Using the same simulator for generating the traces and estimating
the cost as defined in Eqs \eqref{eq:cost-exact} and \eqref{eq:tot-cost-exact}
would however be too optimistic and would represent an upper bound on what can
be achieved by a selection strategy based on simulation.

In order to have a
more realistic estimate of the behavior of a selection strategy based on
simulation, we introduce noise in the simulator, as described below.

@@

%
\begin{itemize}
    \label{alg:epsilon}
\item With probability $(1-\epsilon)$, select the policy $P$ that minimizes the cost over previous time periods (exploitation mode):
%
\begin{equation}
\label{eq:select-greedy}
P = \mbox{argmin}_{P_i, 1 \le i \le 12} w(\rightarrow T;P_i)
\end{equation}
%
\item With probability $\epsilon$, select a policy $P_i, \, 1 \le i \le 12$, at random (exploration mode).
\end{itemize}

Figure~\ref{fig:bandit} illustrates this process. Several studies study the
decay of $\epsilon$ over time, the exploration being less important once the
estimates for the different policies are reliable \cite{Tokic:2010}. This
strategy has however not been beneficial in our case. We believe this is due to
the properties of the traces we use, as explained in
Section~\ref{sec:experiments}. The $\epsilon$-greedy strategy is known to be
outperformed in terms of regret by other classical algorithms such as the UCB
or EXP family of algorithms. See~\cite{bubnow} for a precise definition and
thorough treatment of this subject. These algorithms however all rely on
pre-normalized rewards. Here, the scale of $w_{\epsilon}(t;P_i)$ is not known
in advance. While the usual doubling tricks can be devised to go around
sequential issues of scale with good asymptotical performance, they ruin
performance in practice. Accordingly, we only perform experiments using the
simple $\epsilon$-greedy method.

\begin{figure*}[]
  \centering
  \input{dia/_build/bandit.tex}

  \caption{Illustration of the bandit-based strategy. Every week,
  the wokload from the past week is used to run simulations using every
  reordering policy. The "model" $w$ is updated according
  to~\eqref{eq:tot-cost-greedy} and the policy for the next week is chosen
  according to~\eqref{alg:epsilon}. We denote by $P_{\mbox{bandit},t}$ the 
  policy chosen by the bandit at week $t$.
  }.

  \label{fig:bandit}
\end{figure*}
